---
layout: post
title: A Lady Tasting Tea
---

```{r}
library(tidyverse)
library(mosaic)
```

## Setup



$$
P(\text{correct}) = \frac{\text{Number of way to be correct}} {\text{Total number of outcomes}}
$$ 

## Determining the total number of outcomes

If we have eight cups there are eight ways we can choose one cup. 
How many ways are there to choose two cups from eight?
Let's break this problem down.
We decided there are eight ways to choose the first cup. 
Because we can't choose the same cup twice, that removes the first cup from the list of possible choices for the second cup.
So, we have one less to choose from, leaving seven possible choices for the second cup. 
To determine the number of ways to choose two cups from eight we simply multiple these to numbers (8 * 7 = 56).

```{r}
cups <- 1:8 # We can use integers to label the eight cups.
r <- 4 # Number of correct quesses.
n <- 8 # Total number of cups of tea.
```

First, lets determine the number of possible outcomes for which we can pick 4 cups out of eight.
There are eight ways we can select the first cup. 
Or, said differently, we must select the first cup from among the possible eight.
Regardless of which cup we select first, there will be seven ways to select the second cup, because when we remove the first cup only seven remain.
```{r}
x <- replicate(1e5, sample(1:8, 2,  replace = FALSE))
perms <- as.data.frame(t(unique(x, MARGIN = 2)))
names(perms) <- c("C1", "C2")
p <- perms %>% 
  arrange(C1, C2)
pander::pander(p)
```


